Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2017-02-20 artigo/paper.tex
Added finantial acknowledgments
Shrinked some images and tables

\resizebox{\columnwidth}{!}{%
    \begin{tabular}{cccccccc@{}m{0pt}@{}}
	\hline 
	\multicolumn{8}{|c|}{\cellcolor{Gray}Application}  &\\[12pt]\cline{1-5}\cline{7-7}
	\multicolumn{1}{|c|}{jQuery} & \multicolumn{1}{c|}{HTML5} & \multicolumn{1}{c|}{CSS3 (Bootstrap)} & \multicolumn{1}{c|}{Signaling} & \multicolumn{1}{c|}{ot.js} & \multicolumn{1}{c|}{\cellcolor{Gray}} & \multicolumn{1}{c|}{adapter.js} & \multicolumn{1}{c|}{\cellcolor{Gray}} &\\[12pt]\hline
	\multicolumn{1}{|c|}{HTTP} & \multicolumn{2}{c|}{User Interface}  & \multicolumn{3}{c|}{WebSocket}    & \multicolumn{2}{c|}{WebRTC}      &\\[12pt]\hline
	\end{tabular}
}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/signaling}
    \caption{Signaling sequence diagram}
    \label{fig:signaling2}
\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{figures/devices.png}
		\caption{Multiple devices per user}
		\label{fig:devices}
	\end{figure}

@@

@@

>>>>

\resizebox{\columnwidth}{!}{%
    \begin{tabular}{cccccccc@{}m{0pt}@{}}
	\hline 
	\multicolumn{8}{|c|}{\cellcolor{Gray}Application}  &\\[2pt]\cline{1-5}\cline{7-7}
	\multicolumn{1}{|c|}{jQuery} & \multicolumn{1}{c|}{HTML5} & \multicolumn{1}{c|}{CSS3 (Bootstrap)} & \multicolumn{1}{c|}{Signaling} & \multicolumn{1}{c|}{ot.js} & \multicolumn{1}{c|}{\cellcolor{Gray}} & \multicolumn{1}{c|}{adapter.js} & \multicolumn{1}{c|}{\cellcolor{Gray}} &\\[2pt]\hline
	\multicolumn{1}{|c|}{HTTP} & \multicolumn{2}{c|}{User Interface}  & \multicolumn{3}{c|}{WebSocket}    & \multicolumn{2}{c|}{WebRTC}      &\\[2pt]\hline
	\end{tabular}
}
\end{table}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/signaling2}
    \caption{Signaling sequence diagram}
    \label{fig:signaling2}
\end{figure}

@@

	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{figures/devices2.png}
		\caption{Multiple devices per user}
		\label{fig:devices}
	\end{figure}

@@

\section*{Acknowledgments}

This work was partially supported by national funds through Fundação para a Ciência e a Tecnologia (FCT) with reference UID/CEC/50021/2013.
This work has received funding from the European Union’s Horizon 2020 research and innovation program under grant agreement No 645342; project reTHINK.

@@

\grid
